% NOTE: This is very inspired by http://www.toofishes.net/blog/latex-resume-follow-up/

\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[stretch=10]{microtype}
\usepackage{hyperref}
\usepackage{tgpagella}
\usepackage{enumitem}
\usepackage{indentfirst}
\pagestyle{empty}

\begin{document}
 
% <header>
\begin{center}
{\huge \textbf{Giorgi Dogadze}}


\vspace{1em}

\href{mailto:g.dogadze@gmail.com}{g.dogadze@gmail.com} 
\ \ \textbullet \ \ 
\href{https://github.com/giorgi-dogadze}{github} 
\ \ \textbullet \ \ 
\href{https://gitlab.com/gdogadze}{gitlab} 
\ \ \textbullet \ \ 
\href{https://www.linkedin.com/in/gdogadze/}{linkedin.com/in/gdogadze}
\ \ \textbullet \ \ 
+995 599 93 29 67\end{center}

% </header>

% <work-experience>
\hrule
\vspace{-1.0em}
\subsection*{Work Experience}
  \begin{itemize}
    \item[]

    {\textbf{Primary Portal} \hfill
    \textbf{London, England}}
  \\
  {\emph{Full Stack Engineer} \hfill \emph{July 2022 - Present}}

  \begin{itemize}[label=\textbullet]
  \itemsep0.5em
  \item Creating the infrastructure, connecting banks and institutional investors for capital markets issuance
  \item Developing backend using Nest.js | Node.js | Terraform | DynamoDB | AWS SQS, SNS, SES, and Lambda.
  \item Working with AWS Amplify / Cognito for fast and secure User Auth for CRUD.
  \item Using/developing our created private npm libraries, like: fully custom UI library (everything covered with test and shown in Storybook) and custom \emph{event-bus} library, which gives us the possibility to share events/information between multiple teams.
  \item Working with microfrontend to display different team products in one place.
  \item Refactoring FE using react-query for cache improvement, which results in faster page loading 
  \item Developed comprehensive unit tests for all Frontend functions, hooks, and components.
  \item Implemented unit and API tests for controllers and services.
  \item Created customized forms using Formik, React-table, and Yup for validation.
  \item Conducted end-to-end (e2e) tests to ensure critical web functionality coverage.
  \item Personally optimized the build time of e2e tests in the CI environment by implementing parallel   \item execution of playwright tests, resulting in a 75% reduction in test duration.
Refactored all e2e tests to follow the recommended pattern, ensuring consistency and improved maintainability.
  \item Personally established an AWS CDC pipeline for historical data storage and its CSV file generation.
  \item Conducted code reviews for fellow developers, ensuring code quality and adherence to best practices within the team.
  \item Actively participated in technical planning sessions, providing insights and contributing to solving complex tasks.  
  \item Languages: JavaScript, TypeScript.
  \item Technologies: React.js, Node.js, NestJS, Terraform, Serverless, DynamoDB, GitLab, AWS.
  \item Libraries: Ramda.js, Testing Library, Jest, Cypress, Formik, React-Query, YarnPNP.
  \item Stats: 150 merged merge requests in the 11 months.

  \end{itemize}


   {\textbf{Temi Cloud} \hfill
      \textbf{Tbilisi, Georgia}}
    \\
    {\emph{Full Stack Engineer} \hfill \emph{September 2020 - June 2022}}

    \begin{itemize}[label=\textbullet]
    \itemsep0.5em
    \item Working on the no-code tool for a community-based marketing platform (Jobs, Courses, Events, Content).
    \item Maintaining a React | TypeScript based component library from fully custom Figma designs (90 core components, 300+ unique components, 60K+ lines of code).
    \item Privately create custom Tree data structure, write recursive functions for different kinds of manipulations, fully covered with unit tests.
    \item Privately refactor Storybook pipeline, add more than 200 missing stories to document all components.
    \item Add Social Authentication(Google, Facebook) pipeline to the platform.
    \item Create course and event pipeline in Business and Community Managers, Admin and Platform.
    \item Refactor state management system, use a custom hook for passing states and memoized functions.
    \item Reviewing code of the other developers in the team.
    \item Developing an event-driven backend using Nest.js | Node.js.
    \item Maintain and create new unit tests for every endpoint and function using Jest(more than 350 unit tests).
    \item Collaborating with Product Owner and Scrum Muster on a daily basis.
    \item Languages: JavaScript, TypeScript, SQL.
    \item Technologies: React.js, Node.js, NestJS, Next.js, PostgreSQL, TypeOrm, Jest, Docker, Git | Github.
    \item Stats: 110 merged pull requests, 1912 commits, 115079 line additions and 41361 deletions in our monorepo in the 8 months.
    \end{itemize}
\end{itemize}
% </work-experience>

% <education>
\hrule
\vspace{-1.0em}
\subsection*{Education}
  \begin{itemize}
    \parskip=1em
      \vspace{0.05em}

    \item[]
    {\textbf{Tbilisi State University}}
     \hfill
     \textbf{Tbilisi, Georgia}
    \\
    {\emph{Bachelor in Computer Science GPA: 3.83}
     \hfill
     \emph{2018 - 2022}}

    \item[]
    {\textbf{Georgian Technical University}}
     \hfill
     \textbf{Tbilisi, Georgia}
    \\
    {\emph{Master in Informatics}
     \hfill
     \emph{2022 - 2024}}
  \end{itemize}
% </education> 

% <skills>
\hrule
\vspace{-1.0em}
\subsection*{Skills}
\begin{itemize}
  \parskip=-0.5em
  \vspace{0.05em}
  \item[] \textbf{Languages:} Georgia, English B2, Russian.
  \vspace{0.5em}
  \item[] \textbf{Tech Stack:} JavaScript, TypesSript, React, Node.js, NestJS, Next.js, SQL, Googling.
\end{itemize}
% </skills>

% <Community>
\hrule
\vspace{-1.0em}
\subsection*{Community}
\begin{itemize}
  \parskip=-0.5em
  \vspace{0.05em}
  \newline \textbf {Medium Article:} \href {https://medium.com/@giorgi-dogadze/%E1%83%A0%E1%83%90-%E1%83%90%E1%83%A0%E1%83%98%E1%83%A1-react-virtual-dom-%E1%83%93%E1%83%90-angular-incremental-dom-dec1488d5393} {React Virtual DOM VS Angular Incremental DOM}{, } \href {https://medium.com/@giorgi-dogadze/the-amazing-life-of-javascript-memory-%E1%83%90%E1%83%9C%E1%83%A3-%E1%83%A2%E1%83%98%E1%83%90%E1%83%9C%E1%83%A8%E1%83%90%E1%83%9C%E1%83%98-9183e20b6cfd} {The amazing life of JavaScript memory}{, } \href {https://medium.com/@giorgi-dogadze/react-rendering-%E1%83%98%E1%83%A1-%E1%83%A1%E1%83%90%E1%83%98%E1%83%93%E1%83%A3%E1%83%9B%E1%83%9A%E1%83%9D%E1%83%94%E1%83%91%E1%83%90%E1%83%9C%E1%83%98-6406b3ae67b9} {React Rendering}
  \vspace{0.05em}
  \newline \textbf {TSU Computer Science students conference:} \href {https://computing.tsu.ge/ka/news/15} {Preprocessor directives in C++}
  
\end{itemize}
% </Community>

\end{document}